### 2017-03-09 real/draft.tex
[draft] Add and describe comparison plot

Let's consider the extreme case $\npack \to \infty$ so we can neglect
the uncertainty on $\alpha, \beta$ and
$p(\alpha, \beta \cond \npack, \bml) =
\delta(\alpha-\alpha_0)\delta(\beta - \beta_0)$ such that
\begin{align}
  \lleq{gmj}
  p(Q\cond n,\bml)
  &=     \sum_{N=0}^\infty p(N\cond n) p(Q\cond N, \alpha_0, \beta_0) \, .
\end{align}
For illustration only, let us consider the Poisson rate $\lambda$ were
known. Then learning $n$ would not improve our knowledge of $\lambda$
and we would have
\begin{align}
  \lleq{gmk}
  p(Q\cond \lambda,\bml)
  &=     \sum_{N=0}^\infty p(N\cond \lambda) p(Q\cond N, \alpha_0, \beta_0) \, ,
\end{align}
where $p(N \cond \lambda)$ is the Poisson distribution \refeq{pmb}.
In \reffig{comp-unc}, we illustrate the impact of the uncertainty due
to $\lambda$ or $\alpha, \beta$ for $n=2$ packets and continue to use
as true values $\alpha_0 = 1.5, \beta_0 = 60$. The standard error
increases from 0.042 ($\lambda, \alpha, \beta$ fixed) over 0.059
($\alpha, \beta$ fixed) to 0.11 (nothing fixed).
%
\fred{I guess this is for $n=2$? To what is $\lambda$ fixed? Redo the
  numbers for the actual prior. Add a plot for larger $n$ to show that
  the Poisson completely dominates}
%
The case where all
parameters are known is not attainable in practice and only shown for
comparison. But the case where $\alpha, \beta$ are fixed can be reached easily
if many packets from other bins can be combined. Note that $n=2$ is the
minimum number of packets to perform the binned analysis.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.44\textwidth]{comp_unc_0}
  \includegraphics[width=0.44\textwidth]{comp_unc_2}
  \caption{Prediction considering $\lambda, \alpha, \beta$ fixed (green), $\alpha, \beta$ fixed (red), or nothing fixed (blue).}
  \label{fig:comp-unc}
\end{figure}

>>>>

Let's consider the extreme case $\npack \to \infty$ so we can neglect
the uncertainty on $\alpha, \beta$ and
$p(\alpha, \beta \cond \npack, \bml) =
\delta(\alpha-\alpha_0)\delta(\beta - \beta_0)$ such that
\begin{align}
  \lleq{gmj}
  p(Q\cond n, \alpha_0, \beta_0)
  &=     \sum_{N=0}^\infty p(N\cond n) p(Q\cond N, \alpha_0, \beta_0) \, .
\end{align}
For illustration only, let us consider the Poisson rate $\lambda$ were
known. Then learning $n$ would not improve our knowledge of $\lambda$
and we would have
\begin{align}
  \lleq{gmk}
  p(Q\cond \lambda, \alpha_0, \beta_0)
  &=     \sum_{N=0}^\infty p(N\cond \lambda) p(Q\cond N, \alpha_0, \beta_0) \, ,
\end{align}
where $p(N \cond \lambda)$ is the Poisson distribution \refeq{pmb}.
In \reffig{comp-unc}, we illustrate the impact of the uncertainty due
to $\lambda$ or $\alpha, \beta$ for $n=0,2, 20$ packets and continue
to use as true values $\alpha_0 = 1.5, \beta_0 = 60$. For $n>0$, we
set $\lambda=n$ and for $n=0$, we set $\lambda = 0.347$ by solving
\begin{align}
  \lleq{gml}
  p(N=0 \cond \lambda) &= p(N=0 \cond n=0)
\end{align}
such that the contribution at $N=0$ is identical for the Poisson
likelihood and Poisson posterior predictive distribution.

It is interesting to note that the Jeffreys prior for $\alpha, \beta$
leads to an extra mode at $\Lumtot = 0$ visible in the case $n=2$. We
checked that this is true for every individual term in the
\refeq{gmhb}, and the superposition of $p(\Lumtot \cond N, n, \bml)$
for various $N$ further enhances this effect. The reason for the
boundary mode is that $\GammaDist(\Lumtot \cond \alpha, \beta)$ peaks
at the boundary for $\alpha<1$, and peaks away from $\Lumtot=0$ for
$\alpha>1$. As $n$ increases, the likelihood concentrates around
$\alpha=1.5$, hence the distribution becomes unimodal.

Already for $n=20$, it becomes apparent in the right panel of
\reffig{comp-unc} that the uncertainty for $\Lumtot$ is dominated by
the Poisson uncertainty: both $p(Q \cond n, \alpha_0, \beta_0)$ and
$p(Q \cond n, \bml)$ yield a standard error of $\approx 0.19$.

The case where all parameters are known is not attainable in practice
and only shown for comparison. But the case where $\alpha, \beta$ are
fixed can be reached easily if many packets from other bins can be
combined. Note that $n=2$ is the minimum number of packets to perform
the binned analysis.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{comp_unc}
  \caption{Prediction of $\Lumtot$ for $n=0,2,20$ considering $\lambda, \alpha, \beta$ fixed (green), $\alpha, \beta$ fixed (red), or nothing fixed (blue).}
  \label{fig:comp-unc}
\end{figure}
